Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-07 paper/paper_new.tex

\subsection{Image Contrast}
The contrast of an image is an important image property needed
for the analyses of the BGNN study. Ideally, for INHS images the fish should be well lit and clearly displayed, and the background should also be as light and white as possible.
% Figure~\ref{fig:histo} shows the distribution of
The difference between
the mean intensity of the foreground (i.e.\ the pixels of the fish) and the mean intensity of the background within the fish's bounding box
was computed for all 7,244 images.
The overall mean of the differences is \(144.3\), with a standard deviation of \(15.8\). Images on the low end of the distribution exhibit poor foreground--background contrast, and images on the high end likely contain poorly lit specimens.
Images are considered to have ``low'' and
``high'' contrast if their background-foreground difference is greater than
one standard deviation away from the mean; otherwise they are classified as
``medium''.
Examples of each type of image (low, medium, and high contrast) can be seen in Figure~\ref{fig:contrast}.
The left image has a contrast of 103 (low), the middle image 144
(medium), and the right 186 (high).

@@

\subsection{Scale and Length}
Image scale and fish lengths were calculated for \(7,179\) of the images.
For the remaining 65 images, either the fish, the ``2'' and/or the ``3'' on the ruler were not detected.
Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
measured, using ImageJ~\cite{imagejCite}, in the same 100  test images.
% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ~\cite{imagejCite}.
In this subset of images the average error for the scale calculation
was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler. When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well. An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand-measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm). Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/54172}
  \includegraphics[width=0.49\linewidth]{images/54172_mask}
  \caption{A fish for which the masking and measurement process was highly accurate.}
  \label{fig:scale_len}
\end{figure}

>>>>

\subsection{Image Contrast}
The contrast of an image is an important image property needed
for the analyses of the BGNN study. Ideally, for INHS images the fish should be well lit and clearly displayed, and the background should also be as light and white as possible.
% Figure~\ref{fig:histo} shows the distribution of
The difference between
the mean intensity of the foreground (i.e.\ the pixels of the fish) and the mean intensity of the background within the fish's bounding box
was computed for all \(7,244\) images.
The overall mean of the differences is \(144.3\), with a standard deviation of \(15.8\). Images on the low end of the distribution exhibit poor foreground--background contrast, and images on the high end likely contain poorly lit specimens.
Images are considered to have ``low'' and
``high'' contrast if their background-foreground difference is greater than
one standard deviation away from the mean; otherwise they are classified as
``medium''.
Examples of each type of image (low, medium, and high contrast) can be seen in Figure~\ref{fig:contrast}.
The left image has a contrast of 103 (low), the middle image 144
(medium), and the right 186 (high).

@@

\subsection{Scale and Length}
Image scale and fish lengths were calculated for \(7,179\) of the images.
For the remaining 65 images, either the fish, the ``2'' and/or the ``3'' on the ruler were not detected.
Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
measured, using ImageJ~\cite{imagejCite}, in the same 100  test images.
% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ~\cite{imagejCite}.
In this subset of images the average error for the scale calculation
was \(0.89\%\), and the average error for the fish length calculation was \(5.55\%\).
Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler. When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well. An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm). Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/54172}
  \includegraphics[width=0.49\linewidth]{images/54172_mask}
  \caption{A fish for which the masking and measurement process was highly accurate.}
  \label{fig:scale_len}
\end{figure}
